TAPIR: Threaded Application Programming on Intermittant Resources

### 2017-05-09 paper.tex
Trailing whitespace fixes, #authors = 3
Changed font size to 11, added gitignore
Added stuff we whiteboarded to the tex file

\documentclass[10pt]{sensys-proc}

@@

\usepackage{balance}
\usepackage{comment}
\usepackage{xspace}
\usepackage[export]{adjustbox}
\usepackage{wrapfig}
\newcommand{\chain}{Chain\xspace}
%\numberofauthors{1}

@@

\title{Chains on Threads on Tasks on Channels....}

@@

\section{Introduction/Background}
  \label{sec:intro}
Intro stuff about intermittence that Brandon already knows but we should record for the
heck of it. Here's a sample citation for totally unrelated things~\cite{RC,Grace}!

@@

\section{Implementation}
We only had to break \chain a little. We promise!

\section{Results}
No really, there will be things here!

>>>>

\documentclass[11pt]{sensys-proc}

@@

\usepackage{balance}
\usepackage{comment}
\usepackage{xspace}
\usepackage[export]{adjustbox}
\usepackage{wrapfig}
\newcommand{\chain}{Chain\xspace}
\numberofauthors{3}

@@

\title{TAPIR: Threaded Application Programming on Intermittant Resources}

@@

\section{Introduction/Background}
  \label{sec:intro}
  Chain, DINO\\
  Multithreading\\
  Intermittance Review\\
  RMW\\
  Example Citation\cite{RC,Grace}!

@@

\section{Related Work}
Operating system work\\
TU delft guys...\\
Energy Align\\

\section{Chain Discussion}
Arrays in channels and why that's bad\\
MAX\_NUM\_DIRTY\_FIELDS\\
Explioting the fact that there isn't a compiler\\

\section{What we did} % TODO change title
Scheduler\\
Interrupts\\
Mutexes\\
User programming model for threads\\
Interrupts\\
Round Robin (alternatives, on reboot)\\
SIMD vs MIMD\\
SIMD w/ channels (you don't get your own registers...etc -
    just channels, since intermittant)\\

\section{Implementation}
We only had to break \chain a little. We promise!
Scheduler Data structures and idempotence (what we broke and why we broke it)\\
Mutexes (Simple, meant for pseudo channels)\\
Interrupts (mucked with IE flags)\\

\section{Results}
No really, there will be things here!
Applications/measurements\\
Blinker (x2)\\
RSA+cukoo\\
No verification\\
Memory overhead (read off compiliation)\\
Performance (\# reboots)\\

\section{Future Work}
Duplicating channels (a little renaming or sharing arrays with mutexes)\\
Optimizations to reduce overhead\\
